---
title: "Sialic Acid S0/S1/S2"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      error = FALSE)
```

```{r}
pkgs = c('dplyr','stringr','reshape2', 'tibble', "Metabase", "DT", "ggplot2", "plotly")
for(pkg in pkgs){
    library(pkg, quietly=TRUE, verbose=FALSE, warn.conflicts=FALSE, 
            character.only=TRUE)
}
load("../apps/app/data/data.rda")
```

Reviewer 1's comment 4:

*ApoC-III in HDL Glycopeptides and related Discussion line 581-591: As known from previous work from Alaupovic, Zilversmit, Havel and others it is well known that the highly glycosylated form of ApoC-III is found on newly secreted TG-rich lipoproteins, which during lipolysis are de-sialated. Only particles containing C-III-0 are directed to receptor mediated uptake. Therefore, it would be interesting to know how the ratio of C-III-0/C-III-1 and C-III-0/C-III-2 changed  between the diets and wether this is significant. This information should be integrated and discussed on the basis of  the mass-spectrometric data and the existing literature.*
    
In the meeting before Christmas, we decided to look at the summarized ApoC3 with 0, 1, and 2 sialic acids, normalizing to 100%. 

```{r}
#checkboxInput('percentage', 'Nornalize glycopeptides into 100%?', TRUE)
radioButtons(
    'percentage', label = "How to normalize the data:", 
     choiceName = c('Use 100%', 'Use Raw'), 
     choiceValues = c(TRUE, FALSE)
)
```

```{r}
glc = data$data$glc$glycans
glc$feature_data = glc$feature_data %>%
    rownames_to_column("FeatureID") %>%
    as_tibble() %>%
    tidyr::extract(
    col = 'Composition (Hex HexNAc Fuc Sia)', 
    into = c('Hex', 'HexNac','Fuc', 'Sia'), 
    regex = "(\\d{1})(\\d{1})(\\d{1})(\\d{1})",
    remove = FALSE
    ) %>% 
    mutate(Glc = str_c(Protein, '_', Sia, 'S')) %>%
    as.data.frame %>%
    column_to_rownames('FeatureID') %>%
    feature_data()
apoc3 = reactive({
    mset = subset_features(glc, glc$feature_data$Protein == 'ApoC3')
    if(input$percentage) {
        mset = transform_by_sample(mset, function(sample){
            sample/sum(sample, na.rm = TRUE)
        })
    }
    summarize_features(mset, 'Glc')
})
```

Summarized total ApoC3 glycopeptides with 0, 1, and 2 sialic acids:

```{r}
output$apoc3 = renderDataTable({
    df1 = apoc3()$conc_table %>%
        t %>% as.matrix %>% as.data.frame %>%
        cbind(apoc3()$sample_table) %>% 
        melt(variable.names = c("Subject", "Treatment", "Timepoint")) %>%
        group_by(Treatment, Timepoint, variable) %>%
        summarize(value = mean(value, na.rm = TRUE)) %>%
        dcast(variable ~ Treatment + Timepoint) %>%
        column_to_rownames("variable")
    
    design = model.matrix(~Treatment * Timepoint + Subject,
                          data = as(glc$sample_table, "data.frame"))
    df2 = mSet_limma(apoc3(), design, coef = 13, p.value = 13)
    cbind(df1, df2[,4:5]) %>%
        datatable(selection = list(mode = "single", selected = 1, target = 'row')) %>%
        formatPercentage(1:4, digits = 2) %>%
        formatRound(5:6, digits = 3) %>%
        formatStyle(columns = 5:6, backgroundColor = "orange") %>%
        formatStyle(
            'pvalue', 
            color = styleInterval(0.05, c('red', 'black'))
        )
}, selection = 'single', server = T)
dataTableOutput('apoc3')
```

Click on the row to see boxplot

```{r}
renderPlotly({
    feature = featureNames(apoc3())[input$apoc3_rows_selected]
    plot_boxplot(apoc3(), feature = feature, x = 'Timepoint', 
                 cols = "Treatment", line = "Subject",  color = "Subject")
})
```


The ratios of ApoC3 glycopeptides with different numbers of sialic acids.


```{r}
apoc3_raw = subset_features(glc, glc$feature_data$Protein == 'ApoC3') %>%
    summarize_features('Glc')
apoc3_ratio = GlycomicsSet(
    conc_table = conc_table(
        rbind(
            `S0/S1` = apoc3_raw$conc_table[1,]/apoc3_raw$conc_table[2,],
            `S0/S2` = apoc3_raw$conc_table[1,]/apoc3_raw$conc_table[3,],
            `S1/S2` = apoc3_raw$conc_table[2,]/apoc3_raw$conc_table[3,]
        )
    ),
    sample_table = sample_table(apoc3_raw$sample_table)
)
df1 = apoc3_ratio$conc_table %>%
        t %>% as.matrix %>% as.data.frame %>%
        cbind(apoc3_ratio$sample_table) %>% 
        melt(variable.names = c("Subject", "Treatment", "Timepoint")) %>%
        group_by(Treatment, Timepoint, variable) %>%
        summarize(value = mean(value, na.rm = TRUE)) %>%
        dcast(variable ~ Treatment + Timepoint) %>%
        column_to_rownames("variable")
    
design = model.matrix(~Treatment * Timepoint + Subject,
                      data = as(glc$sample_table, "data.frame"))
df2 = mSet_limma(apoc3_ratio, design, coef = 13, p.value = 13)
df = cbind(df1, df2[,4:5]) %>%
    datatable(selection = list(mode = "single", selected = 1, target = 'row')) %>%
    formatPercentage(1:4, digits = 2) %>%
    formatRound(5:6, digits = 3) %>%
    formatStyle(columns = 5:6, backgroundColor = "orange") %>%
    formatStyle(
        'pvalue', 
        color = styleInterval(0.05, c('red', 'black'))
    )
output$apoc3_ratio = renderDataTable(
    df, server = T, selection = 'single', selected = 1
)
dataTableOutput('apoc3_ratio')
```

```{r}
renderPlotly({
    feature = featureNames(apoc3_ratio)[input$apoc3_ratio_rows_selected]
    plot_boxplot(apoc3_ratio, feature = feature, x = 'Timepoint', 
                 cols = "Treatment", line = "Subject",  color = "Subject")
})
```
